Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-05 to_do_list.tex
Update to-do list. Refer to 'dynamic four-player model' in the text.
revise to-do list for final big re-write of main section of draft

\vskip.3in
Kristy
\begin{itemize}
	\item Think through reviewer 2's suggestion about uncertainty
		\begin{itemize}
			\item How would model actually work with asymmetric information?
		\end{itemize}
	\item Take indecisive war to decisive war
	\item Change sign on payoff functions for $c$ and $p$
	\item Homogenize discount factors
	\item Decide on Reviewer 1's suggestion to recast Proposition 1 as a ``class of games'' instead of ``sufficient conditions''
		\begin{itemize}
			\item ``I understand why the set of sufficient conditions in this proposition is the key result. However, these mechanisms are essentially just assumptions on payoffs; and therefore I would be inclined to interpret these conditions as characterizations of “a class” of games, where this class would satisfy all the assumptions on payoffs (instead of saying sufficient conditions). \\
				I would recommend clearing up Section 3.1 in terms of packaging the results: 
					\begin{enumerate}
						\item First, I would identify a class of games that satisfy the assumptions on payoffs (sufficient conditions (1) through (6) in Proposition 1). Denote this class as G for example. 
						\item Then, formally define the “status quo” equilibrium – an equilibrium in which the equilibrium outcome is perpetual unrecognized statehood with all the actors’ strategies specified. 
						\item Finally, I would state a much clearer and simpler proposition, e.g., For any game G, there exists a status quo equilibrium. ... Then subsection 3.2 would basically be a discussion of this class of games. 
					\end{enumerate}
		\end{itemize}
	\item Clearly specify punishments / equilibrium path to satisfy editor
		\begin{itemize}
			\item ``Clear and detailed description of the noncooperative game''
			\item ``I would also like to see the key logic laid out better in the text, and the full
equilibrium strategy profiles noted so that it is clear how the players are rewarding and punishing each other on and off the equilibrium path''
		\end{itemize}
	\item State process governing status-quo payoffs clearly
		\begin{itemize}
			\item ``If I understand correctly, expenditure R by the patron is essentially a long-term investment that raises the status-quo payoff of the secessionist elite by R in every future period. I suggest stating it this way: The per-period status quo payoff is a state variable; its transition from one period to the next involves an automatic reduction by mu (for the reasons you discuss) and an increase by the amount of the patron's investment.
		\end{itemize}
	\item Make sure equilibrium concept is clearly stated and defined
		\begin{itemize}
			\item ``Because the model is not a repeated game, due to the state variable just described, it may be a bit confusing to some readers, and so it is important to provide formal definitions and to clearly describe the equilibrium concept being utilized. It seems to me that, as Referee 2 states, you are using the Markov perfect equilibrium concept.''
		\end{itemize}
\end{itemize}

@@

	\item R1: Talk to Kristy about whether we want to offer a numerical example a la what R1 requests.

>>>>

\vskip.3in
Kristy
\begin{itemize}
	\item Recast Proposition 1 as a ``class of games'' instead of ``sufficient conditions'' (Reviewer 1)
		\begin{itemize}
			\item ``interpret these conditions as characterizations of “a class” of games, where this class would satisfy all the assumptions on payoffs (instead of saying sufficient conditions).
			\item I would recommend clearing up Section 3.1 in terms of packaging the results: 
					\begin{enumerate}
						\item First, I would identify a class of games that satisfy the assumptions on payoffs (sufficient conditions (1) through (6) in Proposition 1). Denote this class as G for example. 
						\item Then, formally define the “status quo” equilibrium – an equilibrium in which the equilibrium outcome is perpetual unrecognized statehood with all the actors’ strategies specified. 
						\item Finally, I would state a much clearer and simpler proposition, e.g., For any game G, there exists a status quo equilibrium. ... Then subsection 3.2 would basically be a discussion of this class of games. 
					\end{enumerate}
		\end{itemize}
	\item Clearly specify punishments / equilibrium path to satisfy editor
		\begin{itemize}
			\item ``Clear and detailed description of the noncooperative game''
			\item ``I would also like to see the key logic laid out better in the text, and the full
equilibrium strategy profiles noted so that it is clear how the players are rewarding and punishing each other on and off the equilibrium path''
		\end{itemize}
	\item Make sure equilibrium concept is clearly stated and defined
		\begin{itemize}
			\item ``Because the model is not a repeated game, due to the state variable just described, it may be a bit confusing to some readers, and so it is important to provide formal definitions and to clearly describe the equilibrium concept being utilized. It seems to me that, as Referee 2 states, you are using the Markov perfect equilibrium concept.''
		\end{itemize}
	\item Think through reviewer 2's suggestion about uncertainty [DONE]
		\begin{itemize}
			\item How would model actually work with asymmetric information? [NOT GOING TO DO]
		\end{itemize}
	\item Take indecisive war to decisive war [DONE]
	\item Change sign on payoff functions for $c$ and $p$ [DONE]
	\item Homogenize discount factors [DONE]
	\item State process governing status-quo payoffs clearly [DONE]
\end{itemize}

@@

	\item R1: Talk to Kristy about whether we want to offer a numerical example a la what R1 requests. [DONE]
